\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-04 doc/paper.tex
merge "Numeric tests" section into last "Tests" section
add conclusions and acknowledgments

\section{Run-time comparison with other spectrum generators}
\label{sec:comparison}

@@

\appendix
\section{Numeric tests}

@@

>>>>

\section{Tests and comparisons with other spectrum generators}
\label{sec:comparison}

\subsection{Run-time comparison}

@@

\subsection{Numeric tests}

@@

\section{Conclusions}

We presented \fs, a Mathematica package, which generates fast and
modular spectrum generators for non-minimal SUSY models.  [TODO:
That's basically all, but we could add more.]

\section*{Acknowledgments}

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug fixing.
Finally the authors thank Philip Diessner for testing and identifying
bugs in the MRSSM model file, as well as Ulrik Günther for compilation
tests on MacOS.

\appendix
